### 2023-11-21 thesis/sections/2-background.tex
background

@@

In a language game, multiple agents need to solve a task by communicating with each other.
The means of communication are very restricted.
Typically, the agents are given a set of arbitrary symbols, a vocabulary, the agents can use to convey information.
These symbols initially don't have any meaning, but by using and interpreting symbols repeatedly to solve the task the agents learn to use certain symbols, to encode specific information.
By this, a new artificial language emerges between these agents.
The emergence of a language however is highly dependent on the constraints posed on (1) the agents' architectures, (2) the way of communication, (3) the perceptual input for the agents and (4) the task, they need to solve.

>>>>

The study of the emergence of an artificial language serves multiple goals.
First, the study of the emergence of artificial language can help to shed light into why and how natural languages evolved \citep{Bartlett2005,Kirby2002,Kirby2008,Noukhovitch2021}.
This approach allows a deep study of the constraints and restrictions that are necessary that symbols start to be connected with meaning and get grounded in the real world.
Insights in this field might give indications, under which circumstances natural language evolves.
On the other hand, research analyzes how the emerged language looks and how the agents represent information in messages and symbols \citep{Baroni2022,Lazaridou2017,Chaabouni2022,Kottur2017}.
Some studies observe different properties of the emerged languages, such as compositionality, complexity or efficiency, and study how the agents can be biased towards producing a language that holds certain properties.
Eventually, this can produce languages that agents can use in practical applications instead of relying on predefined unflexible protocols.

In a language game, multiple agents need to solve a task by communicating with each other.
The means of communication are very restricted.
Typically, the agents are given a set of arbitrary symbols, a vocabulary, the agents can use to convey information.
These symbols initially don't have any meaning, but by using and interpreting symbols repeatedly to solve the task the agents learn to use certain symbols, to encode specific information.
By this, a new artificial language emerges between these agents.
The emergence of a language however is highly dependent on the constraints posed on (1) the agents' architectures, (2) the way of communication, (3) the perceptual input for the agents and (4) the task, they need to solve \citep{Baroni2022}.

@@
